The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-05-16 ms/ms.tex
overleaf

\journalname{Journal of Advances in Modeling Earth Systems (JAMES)}

\begin{document}

\title{The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble}

\authors{D. Kennedy\affil{1} and many more}

\affiliation{1}{Climate and Global Dynamics Laboratory, NCAR, Boulder, CO, USA.}

\correspondingauthor{Daniel Kennedy}{djk2120@ucar.edu}

\begin{keypoints}
\item enter point 1 here
\item enter point 2 here
\item enter point 3 here
\end{keypoints}

@@

\section{Introduction}

Water availability, land temperature extremes, fire risk, and crop productivity will all see impacts from climate change, and are among the many processes represented within land components of Earth System Models.
Understanding how these processes respond directly and indirectly to CO$_2$ concentrations, and how they themselves impact CO$_2$ concentrations, is at the center of climate change research.  
Our certainty in climate model projections varies by domain and generally decreases with extended time horizons \cite{koven2022}.
Centennial-scale estimates of the cumulative terrestrial carbon sink have been especially challenging, with high uncertainty persisting across model generations \cite{friedlingstein2014,arora2020}. 
A portion of this uncertainty is irreducible, inherent to the challenge of predicting vegetation dynamics in a novel climate \cite{bonan2018}.
But with the ever-increasing observational basis from remote sensing, meteorological stations, flux towers, and field campaigns, combined with increasingly comprehensive land surface modelling platforms, we might expect predictions to become more skillful across subsequent model generations.

>>>>

\journalname{Journal of Advances in Modeling Earth Systems (JAMES)}
\begin{document}
\title{The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble}

\authors{D. Kennedy\affil{1} and ...}

\affiliation{1}{Climate and Global Dynamics Laboratory, NCAR, Boulder, CO, USA.}
\correspondingauthor{Daniel Kennedy}{djk2120@ucar.edu}

\begin{keypoints}
\item enter point 1 here
\end{keypoints}

@@

\section{Introduction}
Water availability, land temperature extremes, fire risk, and crop productivity will all see impacts from climate change, and are among the many processes represented within land components of Earth System Models.
Understanding how these processes respond directly and indirectly to CO$_2$ concentrations, and how they themselves impact CO$_2$ concentrations, is a critical facet of climate change research.  
Our certainty in climate model projections varies by domain and generally decreases with extended time horizons \cite{koven2022}.
Centennial-scale estimates of the cumulative terrestrial carbon sink have been especially challenging, with high uncertainty persisting across model generations \cite{friedlingstein2014,arora2020}. 
A portion of this uncertainty is irreducible, inherent to the challenge of predicting vegetation dynamics in a novel climate \cite{lovenduski2017}.
But with the ever-increasing observational basis from remote sensing, meteorological stations, flux towers, and field campaigns, combined with increasingly comprehensive land surface modelling platforms, we might expect predictions to become more skillful across subsequent model generations.
